### 2014-08-01 paper/paper.tex
Got the program to spit out the number of features regardless if word selection is on. Added a colum to the table
Moved the argument outside. Ditched non-relevant data

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c||r|r|r|r|}
        \hline
                               & Positive & Neutral & Negative & Overall \\
        \hline
        \textit{a}, \textit{i} & 14.85    & 14.06   & 15.10    & 14.49 \\
        \textit{b}, \textit{j} & 14.91    & 14.30   & 15.30    & 14.67 \\
        \textit{c}, \textit{k} & 15.95    & 15.40   & 16.33    & 15.73 \\
        \textit{d}, \textit{l} & 17.13    & 16.86   & 17.41    & 17.04 \\
        \textit{e}, \textit{m} & 18.54    & 17.81   & 18.82    & 18.22 \\
        \textit{f}, \textit{n} & 18.43    & 17.87   & 18.85    & 18.21 \\
        \textit{g}, \textit{o} & 19.64    & 19.15   & 20.05    & 19.46 \\
        \textit{h}, \textit{p} & 20.65    & 20.45   & 20.96    & 20.58 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{The average number of features in each experiment}
    \label{table:numfeatures}
\end{table}

@@

>>>>

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c||r|r|r|r|r|}
        \hline
                               & Positive & Neutral & Negative & Overall & Total \\
        \hline
        \textit{a}, \textit{i} & 14.85    & 14.06   & 15.10    & 14.49   & 5964 \\
        \textit{b}, \textit{j} & 14.91    & 14.30   & 15.30    & 14.67   & 7493 \\
        \textit{c}, \textit{k} & 15.95    & 15.40   & 16.33    & 15.73   & 0 \\
        \textit{d}, \textit{l} & 17.13    & 16.86   & 17.41    & 17.04   & 0 \\
        \textit{e}, \textit{m} & 18.54    & 17.81   & 18.82    & 18.22   & 5993 \\
        \textit{f}, \textit{n} & 18.43    & 17.87   & 18.85    & 18.21   & 7522 \\
        \textit{g}, \textit{o} & 19.64    & 19.15   & 20.05    & 19.46   & 0 \\
        \textit{h}, \textit{p} & 20.65    & 20.45   & 20.96    & 20.58   & 0 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{`Positive', `Neutral', `Negative', and `Overall' refer to the
    average number of features per Tweet in each experiment. `Total' refers to
    the total number of different features in the dataset}
    \label{table:numfeatures}
\end{table}

% TODO finish table

@@

\subsection{Most Informative Features}

\begin{verbatim}
  -3.176 excited==True and label is 'neutral'
   2.328 lied==True and label is 'negative'
   2.279 availability==True and label is 'negative'
  -2.258 excited==True and label is 'negative'
  -2.180 EM_HAPPY==True and label is 'negative'
  -2.171 happy==True and label is 'neutral'
  -2.098 birthday==True and label is 'negative'
   2.016 shitty==True and label is 'negative'
  -1.836 8th==True and label is 'positive'
  -1.801 international==True and label is 'positive'
   1.789 embarrassing==True and label is 'negative'
  -1.762 went==True and label is 'negative'
   1.702 releases==True and label is 'negative'
  -1.672 love==True and label is 'negative'
   1.650 lack==True and label is 'negative'
   1.650 oneil==True and label is 'neutral'
  -1.638 fun==True and label is 'neutral'
   1.599 replay==True and label is 'negative'
  -1.585 great==True and label is 'neutral'
   1.577 asses==True and label is 'positive'
   1.570 garlic==True and label is 'negative'
  -1.564 pass==True and label is 'negative'
   1.560 den==True and label is 'negative'
   1.560 accepting==True and label is 'negative'
  -1.557 sure==True and label is 'negative'
   1.551 insensitive==True and label is 'negative'
   1.547 calvin==True and label is 'negative'
   1.532 jailed==True and label is 'negative'
   1.520 lookin==True and label is 'neutral'
   1.515 2c==True and label is 'negative'
\end{verbatim}
